---
title: "Briefing Paper"
editor: visual
date: "`r Sys.Date()`"

format: 
  html:
    toc: true  # Enable table of contents
    toc-title: "Table of Content"  # Set the title of the ToC
    toc-depth: 2  # Set the depth of headers (h1 and h2)
    toc-location: right
    embed-resources: true
    smooth-scroll: true
    lightbox: true

execute:
  echo: false      # Hide code
  warning: false   # Hide warnings
  message: false   # Hide messages
  results: hide    # Hide output
  
theme:
  light: flatly
  dark: darkly
---

```{r}
#| echo: false
#| results: hide
#| message: false
#| warning: false
library(readxl)
library(writexl)
library(janitor)
library(dplyr)
library(tidyr)
library(janitor)
#install.packages("ggplot2")
#install.packages("kableExtra")
library(kableExtra)
library(knitr)
library(lubridate)
library(stringr)
#install.packages("quantmod")
library(quantmod)
#install.packages("outliers")
library(outliers)
library(ggplot2)
library(htmltools)

#Loading the data frame
df <- read_excel("../Samples/agg_briefing_paper.xlsx", col_names = FALSE)

#Setting up the data frame

titles <- df[1:2,]

colnames(df) <- df [2,]

df_1 <- df[-c(1,2),]

#converting all numeric date variables to dates

df_1 <- df_1 %>% 
  mutate(across(c(`_submission_time`,today, Q45_1, Q25,Q165, Q141_3, S1_3, S2_3, S3_3, S4_3), ~ as.numeric(.))) %>%
  mutate(across(c(`_submission_time`,today, Q45_1), ~ excel_numeric_to_date(.)))%>%
  mutate(Q133 = ifelse(grepl("^Yes",Q133), "Yes", Q133))%>%
  mutate(Q14 = if_else(Q14 == "Sikasso", "Sikasso city", Q14))
```

# Grouping Variables

```{r}
df_1 %>% 
  mutate(Q133 = ifelse(grepl("^Yes",Q133), "Yes", Q133)) %>%
  tabyl(Q133, Q27) %>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  
  #Nice formatting
  adorn_title(row_name = "Smuggler use", col_name = "Gender", "combined") %>%
  
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Grouping Variables","","",""),align = "l")
```

# Profiling

## Q13 - country of interview

```{r}
df_1 %>% 
  tabyl(Q13,Q27) %>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country ", col_name = " Gender", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

## Q14 - Place of interview

```{r}
tabyl_result <- df_1 %>%
  tabyl(Q14, Q133, Q27) 

total_tabyl <- df_1 %>%
  tabyl(Q14) %>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Place of interview", "", ""),align = "l")

# Format the Female table
female_table <- tabyl_result$Female %>%
  arrange(desc(Yes+No))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Location ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  arrange(desc(Yes+No))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Location ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
total_tabyl
male_table
female_table

```

## Q25 - Age - Summary

```{r}
df_1 %>%
  summarize(across(Q25, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("Q25_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Age", "", "",""),align = "l")

df_age <- df_1 %>%
  filter(!is.na(Q25))

# Create age groups (e.g., 5-year intervals)
df_age <- df_age %>%
  mutate(age_group = cut(Q25, breaks = seq(0, 100, by = 5), right = FALSE))

# Summarize the data by age group
df_age_summary <- df_age %>%
  group_by(age_group) %>%
  summarise(count = n()) %>%
  ungroup()
```

------------------------------------------------------------------------

```{r}

# Create the pyramid plot
ggplot(df_age_summary, aes(x = age_group, y = count)) +
  geom_bar(stat = "identity", fill = "#2596be") +  # You can change the color
  geom_text(aes(label = count), hjust = -0.1, size = 4, alpha = 0.6) +
  coord_flip() +
  labs(
    title = "Age Distribution of Respondents",
    x = "Age Group",
    y = "Number of Respondents"
  ) +
  theme_minimal() +
  theme(
  axis.title.x = element_text(margin = margin(t = 15)),  # Add margin to the x-axis title
  axis.title.y = element_text(margin = margin(r = 15)),   # Add margin to the y-axis title
  plot.title = element_text(hjust = -0.15)
  )
```

## Q27 - Sex

```{r}
df_1 %>%
  tabyl(Q27, Q133) %>%
  arrange(desc(Yes +No))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Sex ", col_name = " Smuggler use", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

## Q30 - Dependent children

```{r}
tabyl_result <- df_1 %>%
  tabyl(Q30, Q133, Q27) 

total_tabyl <- df_1 %>%
  tabyl(Q30) %>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Carrying dependent children", "", ""),align = "l")

# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Carrying dependent children ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Carrying dependent children ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
total_tabyl
male_table
female_table
```

## Q31 - country of origin

```{r}
tabyl_result <- df_1 %>%
  filter(Q31 %in% c("Togo","Nigeria", "Côte d'Ivoire", "Benin", "Niger"))%>%
  tabyl(Q31, Q133, Q27)

total_tabyl <- df_1 %>%
  tabyl(Q31) %>%
  arrange(desc(n))%>%
  head(5)%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Country of origin", "", "N = 2674"),align = "l")

# Format the Female table
female_table <- tabyl_result$Female %>%
  arrange(desc(Yes+No))%>%
  adorn_totals(where =c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country of origin ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  arrange(desc(Yes+No))%>%
  adorn_totals(where =c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country of origin ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
total_tabyl
male_table
female_table


```

## Q33 - migration status

```{r}
df_1 %>%
  tabyl(Q33, Q133) %>%
  arrange(desc(Yes +No))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Migration status ", col_name = " Smuggler use", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

# 1- How does the use of smuggling services influence the choice of migration routes?

## Q41 - country of departure

```{r}
tabyl <- df_1 %>%
  tabyl(Q41, Q133) %>%
  arrange(desc(Yes +No))%>%
  head(10)%>%
  adorn_totals(where = c("row", "col"))

tabyl%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front", ns=tabyl)%>%
  adorn_title(row_name = "Country of departure ", col_name = " Smuggler use", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

## Q45_1 - duration of journey at the interview date

```{r}
df_1 %>%
  mutate(journey_duration = difftime(df_1[["today"]],Q45_1))%>%
  mutate(journey_class = case_when (
    journey_duration < 30 ~ "Less than a month",
    journey_duration < 120 ~ "Between 1 to 6 months",
    journey_duration < 365 ~ "Between 6 to 12 months",
    TRUE ~ "More than a year"
  ))%>%
  tabyl(journey_class,Q133)%>%
  arrange(desc(Yes+No))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Duration of journey ", col_name = " Smuggler use", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

## Transit Journey

### Transited vs Passed directly

```{r}

tabyl_result <-df_1 %>%
  mutate(transited = case_when(
    Q47 == "None" ~ "Passed directly",
    TRUE ~ "Transited at least one country"
  ))%>%
  tabyl(transited,Q133,Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))



total_tabyl <- df_1 %>%
  mutate(Transited = case_when(
    Q47 == "None" ~ "Passed directly",
    TRUE ~ "Transited at least one country"
  ))%>%
  tabyl(Transited)%>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("", "", "N = 2674"),align = "l")
  
  
  
# Format the Female table
female_table <- tabyl_result$Female %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_result$Female)%>%
  adorn_title(row_name = "Transited ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_result$Male)%>%
  adorn_title(row_name = "Transited ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")




total_tabyl
male_table
female_table

```

### Q47\>Q54 - Countries transited

```{r}
tabyl <- df_1 %>%
  select(`_id`,Q47:Q54,Q133)%>%
  select(-matches("_1"))%>%
  select(where(~!all(is.na(.))))%>%
  pivot_longer(cols = -c(`_id`,Q133), values_to = "countries_transited")%>%
  distinct(`_id`, countries_transited , .keep_all = TRUE) %>%
  filter(!is.na(countries_transited), countries_transited !="None")%>%
  tabyl(countries_transited,Q133)%>%
  arrange(desc(Yes+No))%>%
  head(10)%>%
  adorn_totals(where =c("row", "col"))

tabyl %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front", ns = tabyl)%>%
  adorn_title(row_name = "Countries transited ", col_name = " Smuggler use", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

N= number of people who said having transited at least once

## Stops

### Stopped at least once vs did not stop

```{r}
df_1 %>%
  mutate(transited = case_when(
    Q56 == "None" ~ "Did not stop at all",
    TRUE ~ "Stopped at least once"
  ))%>%
  tabyl(transited,Q133)%>%
  arrange(desc(Yes + No))%>%
  adorn_totals(where =c("row", "col"))%>%  
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Stopped ", col_name = " Smuggler use", "combined") %>%
  knitr::kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
  
```

### Summary of stop per subset

```{r}
df_stops <- df_1 %>%
  select(Q133,Q56,Q59,Q62,Q65,Q68)%>%
  mutate(count = rowSums(across(everything(), ~ !(. %in% c("Yes", "No", "None", NA )))))


df_stops %>%
  filter(Q133 == "Yes" & count != 0)%>%
  summarize(across(count, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("count_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l", caption = "Stops for those who used a smuggler") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")

df_stops %>%
  filter(Q133 == "No" & count != 0)%>%
  summarize(across(count, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("count_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l", caption = "Stops for those who did not use a smuggler") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

### Countries \> Top 5 locations per country

```{r}
countries <- df_1 %>%
  pivot_longer(cols = c(Q56,Q59,Q62,Q65,Q68), names_to = "country_stop_rank", values_to = "country_stops")%>%
  select(Q133,country_stops)


locations <- df_1 %>%
  pivot_longer(cols = c(Q57,Q60,Q63,Q66,Q69), names_to = "location_stop_rank", values_to = "location_stops")%>%
  select(location_stops)

countries_locations <- cbind(countries,locations)

tabyl_ref <- countries_locations %>%
  filter(if_all(c(country_stops, location_stops), ~ !is.na(.) & . != "None" & . != "Other"))%>%
  tabyl(country_stops,location_stops)%>%
  pivot_longer(-country_stops, names_to = "location_stops", values_to = "n") %>%  # Make it long
  arrange(desc(n))%>%
  filter( !(n < 25))

tabyl_result <- countries_locations %>%
  filter(if_all(c(country_stops, location_stops), ~ !is.na(.) & . != "None" & . != "Other"))%>%
  filter(location_stops %in% tabyl_ref$location_stops)%>%
  tabyl(country_stops,location_stops,Q133)%>%
  lapply(function(df) {
    pivot_longer(df,-country_stops, names_to = "location_stops", values_to = "n")
    })%>%
  lapply(function(df) arrange(df,country_stops, desc(n)))


tabyl_ref%>%
  adorn_totals(where = "row")%>%
  mutate(percent = n / 5866)%>%
  adorn_pct_formatting(column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")%>%
  add_header_above(header = c("Country/Location stops", "", "","N = 5866"),align = "l")


tabyl_no <- tabyl_result$No%>%
  filter(n !=0)%>%
  knitr::kable(caption = "Respondents that did not use a smuggler", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")%>%
  add_header_above(header = c("Country/Location stops", "", ""),align = "l")

tabyl_yes <- tabyl_result$Yes%>%
  filter(n !=0)%>%
  knitr::kable(caption = "Respondents that used a smuggler", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")%>%
  add_header_above(header = c("Country/Location stops", "", ""),align = "l")


tabyl_yes
tabyl_no
```

N= Total number of stops mentioned

### Countries \> Top 5 locations per country \> Top reasons per location

```{r}

reasons_matrix <- df_1 %>% 
  pivot_longer(`Q58/Working to earn money for the next stretch of the journey`: `Q58/Smugglers stopped to recruit clients`, values_to = "reasons") %>%
  select(Q27, Q133,reasons)%>%
  filter(if_all(c(reasons), ~ !is.na(.) & . != "None"))

#aggregating the reasons for the second stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q61/Working to earn money for the next stretch of the journey`: `Q61/Smugglers stopped to recruit clients`, values_to = "reasons") %>%
  select(Q27, Q133,reasons)%>%
  filter(if_all(c(reasons), ~ !is.na(.) & . != "None")) )


#aggregating the reasons for the third stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q64/Working to earn money for the next stretch of the journey`: `Q64/Smugglers stopped to recruit clients`, values_to = "reasons") %>%
  select(Q27, Q133,reasons)%>%
  filter(if_all(c(reasons), ~ !is.na(.) & . != "None")) )


#aggregating the reasons for the fourth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q67/Working to earn money for the next stretch of the journey`: `Q67/Smugglers stopped to recruit clients`, values_to = "reasons") %>%
  select(Q27, Q133,reasons)%>%
  filter(if_all(c(reasons), ~ !is.na(.) & . != "None")) )


#aggregating the reasons for the fifth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q70/Working to earn money for the next stretch of the journey`: `Q70/Smugglers stopped to recruit clients`, values_to = "reasons") %>%
  select(Q27, Q133,reasons)%>%
  filter(if_all(c(reasons), ~ !is.na(.) & . != "None")) )


#Compute frequencies for each reason

reasons_matrix%>%
  tabyl(reasons)%>%
  arrange(desc(n))%>%
  mutate(percent = n/5866)%>%
  adorn_pct_formatting(column = "percent") %>%
  #adorn_totals(where = "row")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Total reasons for choosing stop", "", "N = 5866"),align = "l")



tabyl_ref <- reasons_matrix%>%
  tabyl(reasons, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_ref$Female %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Female)%>%
  adorn_title(row_name = "Reasons for stop ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_ref$Male %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Male)%>%
  adorn_title(row_name = "Reasons for stop ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")




male_table
female_table


######## countries with locations and their top reasons per location

# countries <- df_1 %>%
#   pivot_longer(cols = c(Q56,Q59,Q62,Q65,Q68), names_to = "country_stop_rank", values_to = "country_stops")%>%
#   select(country_stops)
# 
# 
# locations <- df_1 %>%
#   pivot_longer(cols = c(Q57,Q60,Q63,Q66,Q69), names_to = "location_stop_rank", values_to = "location_stops")%>%
#   select(location_stops)
# 
# countries_locations <- cbind(countries,locations)
# 
# df_2 <- cbind(df_1,countries_locations)
# 
# 
# 
# #First stop with location and reasons
# 
# stop_matrix <- df_1 %>%
#   select(Q56:Q58_1)%>%
#   select(-matches("_1"), -c(Q58, `Q58/Refused`, `Q58/Other`))%>%
#   pivot_longer(col = -c(Q56,Q57),  # Pivot all except `country_stops` and `location_stops`
#                names_to = "reasons_stop_rank",
#                values_to = "reasons_stop")%>%
#   filter(if_all(c(reasons_stop), ~ !is.na(.) & . != "None"))%>%
#   select(-reasons_stop_rank)
# 
# 
# #aggregating second stop with location and reasons
# 
# stop_matrix <- rbind (stop_matrix, df_1 %>%
#   select(Q59:Q61_1)%>%
#   select(-matches("_1"), -c(Q61, `Q61/Refused`, `Q61/Other`))%>%
#   pivot_longer(col = -c(Q59,Q60),  # Pivot all except `country_stops` and `location_stops`
#                names_to = "reasons_stop_rank",
#                values_to = "reasons_stop")%>%
#   rename(
#     Q56 = Q59,
#     Q57 = Q60)%>%
#   filter(if_all(c(reasons_stop), ~ !is.na(.) & . != "None"))%>%
#   select(-reasons_stop_rank))
# 
# #aggregating third stop with location and reasons
# 
# stop_matrix <- rbind (stop_matrix, df_1 %>%
#   select(Q62:Q64_1)%>%
#   select(-matches("_1"), -c(Q64, `Q64/Refused`, `Q64/Other`))%>%
#   pivot_longer(col = -c(Q62,Q63),  # Pivot all except `country_stops` and `location_stops`
#                names_to = "reasons_stop_rank",
#                values_to = "reasons_stop")%>%
#   rename(
#     Q56 = Q62,
#     Q57 = Q63)%>%
#   filter(if_all(c(reasons_stop), ~ !is.na(.) & . != "None"))%>%
#   select(-reasons_stop_rank))
# 
# 
# #aggregating fourth stop with location and reasons
# 
# stop_matrix <- rbind (stop_matrix, df_1 %>%
#   select(Q65:Q67_1)%>%
#   select(-matches("_1"), -c(Q67, `Q67/Refused`, `Q67/Other`))%>%
#   pivot_longer(col = -c(Q65,Q66),  # Pivot all except `country_stops` and `location_stops`
#                names_to = "reasons_stop_rank",
#                values_to = "reasons_stop")%>%
#   rename(
#     Q56 = Q65,
#     Q57 = Q66)%>%
#   filter(if_all(c(reasons_stop), ~ !is.na(.) & . != "None"))%>%
#   select(-reasons_stop_rank))
# 
# #aggregating fifth stop with location and reasons
# 
# stop_matrix <- rbind (stop_matrix, df_1 %>%
#   select(Q68:Q70_1)%>%
#   select(-matches("_1"), -c(Q70, `Q70/Refused`, `Q70/Other`))%>%
#   pivot_longer(col = -c(Q68,Q69),  # Pivot all except `country_stops` and `location_stops`
#                names_to = "reasons_stop_rank",
#                values_to = "reasons_stop")%>%
#   rename(
#     Q56 = Q68,
#     Q57 = Q69)%>%
#   filter(if_all(c(reasons_stop), ~ !is.na(.) & . != "None"))%>%
#   select(-reasons_stop_rank))
# 
# stop_matrix <- rename(stop_matrix,
#        Country = Q56,
#        Location = Q57)
# 
# 
# #Compute frequencies for each reason for each country
# 
# stop_matrix%>%
#   filter(Location!="Other")%>%
#   group_by(Country, Location, reasons_stop)%>%
#   summarize(frequency = n())%>%
#   arrange(desc(frequency))%>%
#   group_by(Country) %>%
#   slice_max(order_by = frequency, n = 5)%>%
#   mutate(percent= frequency / 5866) %>%
#   adorn_pct_formatting(column = "percent")%>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
#                 full_width = FALSE,
#                 position = "left")%>%
#   add_header_above(header = c("Country/Location stops", "", "","","N = 5866"),align = "l")
```

## Q72 - Reasons for choosing a route

```{r}
reasons <- df_1 %>%
    select(Q27,Q133,`Q72/Safest`:`Q72/This was the only option`)  %>%
    pivot_longer(cols = - c(Q27,Q133), values_to = "Reasons_for_choosing_route")%>%
    select(-name)%>%
    filter(!is.na(Reasons_for_choosing_route))

reasons%>%
    tabyl(Reasons_for_choosing_route)%>%
    mutate(percent = n/2674)%>%
    arrange(desc(n))%>%
    #adorn_totals(where = "row")%>%
    adorn_pct_formatting(columns = "percent") %>%
    knitr :: kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                  full_width = TRUE, 
                  position = "left")%>%
    add_header_above(header = c("Reasons for choosing_route", "", "N = 2674"),align = "l")



tabyl_result <- reasons %>%
  tabyl(Reasons_for_choosing_route, Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Reasons for choosing route ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Reasons for choosing route ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q22 - end of journey

Removed NA values from the analysis.

```{r}
df_1 %>% 
  tabyl(Q22, show_na = FALSE) %>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("End of journey", "", ""),align = "l")


tabyl_result <- df_1 %>%
  tabyl(show_na = FALSE, Q22, Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "End of journey ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "End of journey ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q92 - Preferred destination

```{r}
tabyl <- df_1 %>% 
  tabyl(show_na = FALSE,Q92, Q133) %>%
  arrange(desc(Yes + No))%>%
  adorn_totals(where = c("row", "col"))

tabyl%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Preferred destination / Smuggler use", "", "", "Removed NAs"),align = "l")
```

## S7 - Reasons for using smuggler services

```{r}
df_1 %>%
  select(`S7/I thought it would be cheaper`:`S7/The smuggler pressured me into it`)  %>%
  pivot_longer(cols = everything(), values_to = "Reasons_for_using_smugglers")%>%
  tabyl(Reasons_for_using_smugglers, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Reasons for using smugglers", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`S7/I thought it would be cheaper`:`S7/The smuggler pressured me into it`)  %>%
  pivot_longer(cols = -Q27, values_to = "Reasons_for_using_smugglers")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, Reasons_for_using_smugglers,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Reasons for using smuggler / Sex", "", "", "Removed NAs"),align = "l")
```

## Q133 - use of smuggler

```{r}
df[-c(1,2),] %>% 
    mutate(across(c(`_submission_time`,today, Q45_1, Q25,Q165, Q141_3, S1_3, S2_3, S3_3, S4_3), ~ as.numeric(.))) %>%
  mutate(across(c(`_submission_time`,today, Q45_1), ~ excel_numeric_to_date(.)))%>%
  mutate(Q14 = if_else(Q14 == "Sikasso", "Sikasso city", Q14))%>%
  filter(Q133 != "No")%>%
  select(Q133, Q27)%>%
  tabyl(Q133,Q27, show_na = FALSE) %>%
  #mutate(percent = n/1550)%>%
  arrange(desc(Female+ Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Use of smuggler / Sex", "", "", "Removed NAs"),align = "l")
```

## Q134 - Types of smuggler services

```{r}
df_1 %>%
  filter(smuggler_module_open == "Yes" )%>%
  select(`Q134/Provision of documents`:`Q134/Helped me find a job`)  %>%
  pivot_longer(cols = everything(), values_to = "Types_smuggler_services")%>%
  tabyl(show_na = FALSE, Types_smuggler_services)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Types of smuggler services", "", "N = 1550"),align = "l")


df_1 %>%
  filter(smuggler_module_open == "Yes" )%>%
  select(Q27,`Q134/Provision of documents`:`Q134/Helped me find a job`)  %>%
  pivot_longer(cols = -Q27, values_to = "Types_smuggler_services")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, Types_smuggler_services,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Types_smuggler_services / Sex", "", "", "Removed NAs"),align = "l")
```

## Smugglers and border crossing

### S10 - use of a smuggler to cross a border

```{r}
df_1 %>%
  select(S10, Q27)%>%
  tabyl(show_na = FALSE, S10,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Use of smuggler to cross a border / Sex", "","", ""),align = "l")
```

### S10_3 - Borders Crossed

```{r}

#Total tabyl
df_1 %>% 
  filter(S10 == "Yes")%>%
  select(Q27,`S10_3/Egypt/Libya`:`S10_3/West - Togo/Burkina Faso`)%>%
  pivot_longer(cols = `S10_3/Egypt/Libya`:`S10_3/West - Togo/Burkina Faso`, values_to = "border_crossed")%>%
  select(-name)%>%
  filter(!is.na(border_crossed))%>%
  tabyl(border_crossed)%>%
  arrange(desc(n))%>%
  head(10)%>%
  adorn_totals(where = c("row"))%>%
  mutate(percent = n /1550)%>%
  adorn_pct_formatting(column = "percent")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Borders crossed with a smuggler", "", "N = 1550"),align = "l")



tabyl <- df_1 %>% 
  filter(S10 == "Yes")%>%
  select(Q27,`S10_3/Egypt/Libya`:`S10_3/West - Togo/Burkina Faso`)%>%
  pivot_longer(cols = `S10_3/Egypt/Libya`:`S10_3/West - Togo/Burkina Faso`, values_to = "border_crossed")%>%
  select(-name)%>%
  filter(!is.na(border_crossed))%>%
  tabyl(border_crossed, Q27)%>%
  arrange(desc(Female + Male))%>%
  head(10)%>%
  adorn_totals(where = c("row", "col"))

tabyl%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl)%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Borders crossed with a smuggler / Sex", "", "",""),align = "l")
```

## S6: predeparture intentions for using smuggling services

```{r}
df_1 %>%
  tabyl( show_na = FALSE,S6,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages()%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("predeparture intentions for using smuggling services / Sex", "", "", ""),align = "l")
```

# 2- How do smuggling fees affect journey costs and financing options?

## Q138: initial finance of the journey

```{r}
df_1 %>% 
  select(`Q138/Borrowing`: `Q138/There was no initial payment`)%>%
  pivot_longer(cols = everything(), values_to = "smuggling_financing")%>%
  select(-name)%>%
  tabyl(show_na = FALSE, smuggling_financing)%>%
  mutate(percent = n/2674)%>%
  arrange(desc(percent))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Ways of financing", "", "N = 2674"),align = "l")


tabyl_result <- df_1 %>% 
  select(Q27, Q133,`Q138/Borrowing`: `Q138/There was no initial payment`)%>%
  pivot_longer(cols = `Q138/Borrowing`: `Q138/There was no initial payment`, values_to = "smuggling_financing")%>%
  select(-name)%>%
  tabyl(show_na = FALSE, smuggling_financing, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Ways of financing ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Ways of financing ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table

```

## Q139: Was this enough money to pay for your journey so far?

```{r}
df_1 %>%
  tabyl(Q139, show_na = FALSE)%>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Enough money?", "Removed NAs", ""),align = "l")


tabyl_result <- df_1 %>% 
  select(Q139,Q27,Q133)%>%
  tabyl(show_na = FALSE, Q139, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))

# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Enough money? ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Enough money? ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q140: How have you paid for the journey since its start?

```{r}
df_1 %>% 
  select(`Q140/I worked`: `Q140/Sold belongings`)%>%
  pivot_longer(cols = everything(), values_to = "ongoing_journey_financing")%>%
  select(-name)%>%
  tabyl(ongoing_journey_financing, show_na = FALSE)%>%
  mutate(percent = n/748)%>%
  arrange(desc(percent))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Financing means of ongoing journey", "", "N = 2674"),align = "l")

tabyl_result <- df_1 %>% 
  select(Q27, Q133,`Q140/I worked`: `Q140/Sold belongings`)%>%
  pivot_longer(cols = `Q140/I worked`: `Q140/Sold belongings`, values_to = "ongoing_journey_financing")%>%
  select(-name)%>%
  tabyl(show_na = FALSE, ongoing_journey_financing, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Ways of financing ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Ways of financing ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q141 - cost of journey - Summary

```{r}
getFX("XOF/USD")
cfa_usd <- as.numeric(last(XOFUSD$XOF.USD))
getFX("EUR/USD")
eur_usd <- as.numeric(last(EURUSD$EUR.USD))

df_1 %>%
  filter(Q141 == "Know the amount" & Q133 == "Yes") %>%
  select(Q141_1, Q141_3) %>%
  mutate(
    Q141_3 = as.numeric(Q141_3),  # Convert the column to numeric
    Q141_3 = case_when(
      Q141_1 == "CFA" ~ round(Q141_3 * cfa_usd),  # Convert CFA to USD
      Q141_1 == "EUR" ~ round(Q141_3 * eur_usd),  # Convert EUR to USD
      TRUE ~ Q141_3  # Keep the original value for other cases
    )
  ) %>%
  filter(Q141_3 != outlier(Q141_3))%>%
  summarize(across(Q141_3, list(Mean = ~paste0(round(mean(., na.rm = TRUE),2), ' $'),
                             Median = ~paste0(median(., na.rm = TRUE),' $'),
                             Min = ~paste0(min(., na.rm = TRUE),' $'),
                             Max = ~paste0(max(., na.rm = TRUE),' $'))))%>%
  rename_with(~ gsub("Q141_3_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(caption = "Respondents that used a smuggler", format = "html",align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Cost of journey", "", "","N = 1471"),align = "l")


df_1 %>%
  filter(Q141 == "Know the amount" & Q133 == "No") %>%
  select(Q141_1, Q141_3) %>%
  mutate(
    Q141_3 = as.numeric(Q141_3),  # Convert the column to numeric
    Q141_3 = case_when(
      Q141_1 == "CFA" ~ round(Q141_3 * cfa_usd),  # Convert CFA to USD
      Q141_1 == "EUR" ~ round(Q141_3 * eur_usd),  # Convert EUR to USD
      TRUE ~ Q141_3  # Keep the original value for other cases
    )
  ) %>%
  filter(Q141_3 != outlier(Q141_3))%>%
  summarize(across(Q141_3, list(Mean = ~paste0(round(mean(., na.rm = TRUE),2), ' $'),
                             Median = ~paste0(median(., na.rm = TRUE),' $'),
                             Min = ~paste0(min(., na.rm = TRUE),' $'),
                             Max = ~paste0(max(., na.rm = TRUE),' $'))))%>%
  rename_with(~ gsub("Q141_3_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(caption = "Respondents that did not use a smuggler", format = "html",align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Cost of journey", "", "","N = 1063"),align = "l")


# Define more granular categories for costs below $500
cost_bins_sub <- c(0, 100, 200, 300, 400, 500, 1000, 2000, 5000, Inf)
cost_labels_sub <- c("$0-$100", "$100-$200", "$200-$300", "$300-$400", "$400-$500", "$500-$1000", "$1000-$2000", "$2000-$5000", "> $5000")

# For smuggler users (Q133 == "Yes") with new subclasses
df_smuggler_sub <- df_1 %>%
  filter(Q141 == "Know the amount" & Q133 == "Yes") %>%
  select(Q141_1, Q141_3) %>%
  mutate(
    Q141_3 = as.numeric(Q141_3),  # Convert to numeric
    Q141_3 = case_when(
      Q141_1 == "CFA" ~ round(Q141_3 * cfa_usd),  # Convert CFA to USD
      Q141_1 == "EUR" ~ round(Q141_3 * eur_usd),  # Convert EUR to USD
      TRUE ~ Q141_3  # Keep the original for USD
    )
    ,
    Cost_Category = cut(Q141_3, breaks = cost_bins_sub, labels = cost_labels_sub)  # Categorize the costs with finer bins
  ) %>%
  filter(!is.na(Cost_Category)) %>%
  count(Cost_Category) %>%
  mutate(Group = "Smuggler", n = -n)  # Negative for mirrored effect

# For non-smuggler users (Q133 == "No") with new subclasses
df_non_smuggler_sub <- df_1 %>%
  filter(Q141 == "Know the amount" & Q133 == "No") %>%
  select(Q141_1, Q141_3) %>%
  mutate(
    Q141_3 = as.numeric(Q141_3),  # Convert to numeric
    Q141_3 = case_when(
      Q141_1 == "CFA" ~ round(Q141_3 * cfa_usd),  # Convert CFA to USD
      Q141_1 == "EUR" ~ round(Q141_3 * eur_usd),  # Convert EUR to USD
      TRUE ~ Q141_3  # Keep the original for USD
    ),
    Cost_Category = cut(Q141_3, breaks = cost_bins_sub, labels = cost_labels_sub)  # Categorize the costs with finer bins
  ) %>%
  filter(!is.na(Cost_Category)) %>%
  count(Cost_Category) %>%
  mutate(Group = "Non-Smuggler")  # Positive for non-smuggler users

# Combine the two datasets for plotting
df_combined_sub <- bind_rows(df_smuggler_sub, df_non_smuggler_sub)

# Calculate the y-axis (count) position with the maximum frequency for each group
max_smuggler_value <- df_combined_sub %>% 
  filter(Group == "Smuggler") %>% 
  arrange(n) %>% 
  slice(1) %>% 
  pull(n)

max_non_smuggler_value <- df_combined_sub %>% 
  filter(Group == "Non-Smuggler") %>% 
  arrange(desc(n)) %>% 
  slice(1) %>% 
  pull(n)

# Create the updated mirrored bar chart with horizontal lines for each group
ggplot(df_combined_sub, aes(x = Cost_Category, y = n, fill = Group)) +
  geom_bar(stat = "identity", position = "identity") +
  
  # Add horizontal lines for the highest frequency for both groups (because of coord_flip())
  geom_hline(yintercept = max_smuggler_value, linetype = "dashed", color = "grey", size = 0.2) +  # Smuggler
  geom_hline(yintercept = max_non_smuggler_value, linetype = "dashed", color = "grey", size = 0.2) +  # Non-Smuggler
  
  
  coord_flip() +  # Flip coordinates for horizontal bars
  scale_y_continuous(labels = abs, breaks = c(max_smuggler_value, max_non_smuggler_value, seq(-250, 250, by = 100))) +
  
  # Customize the y-axis to only show upper boundaries
  scale_x_discrete(labels = c("< $100", "< $200", "< $300", "< $400", "< $500", "< $1000", "< $2000", "< $5000", "> $5000")) +
  
  # Customize the fill colors: change red to light violet
  scale_fill_manual(values = c("Non-Smuggler" = "#D8BFD8", "Smuggler" = "#00CED1")) +
  
  # Labels
  labs(
    x = "Cost of Journey",
    y = "Number of Respondents",
    title = "Journey Costs"
  ) +
  
  # Customize the theme: Legend beneath the x-axis title and justified to the left
  theme_minimal() +
  theme(
    legend.title = element_blank(),  # Hide the "Group" label in the legend
    legend.position = "bottom",  # Move the legend to the bottom
    legend.direction = "horizontal",  # Set legend to be horizontal
    plot.title = element_text(hjust = 0.45),  # Center-align title
    axis.text.y = element_text(size = 10),  # Adjust y-axis text size
    axis.title.x = element_text(margin = margin(t = 15)),  # Add margin to the x-axis title
    axis.title.y = element_text(margin = margin(r = 15)),   # Add margin to the y-axis title
    plot.margin = margin(10, 10, 20, 10)  # Add margin below the plot for the legend
  )



```

N = only those that know the amount

## Q135: Payment modalities of smuggling services

```{r}
df_1 %>%
  filter(Q133 != "No" & smuggler_module_open == "Yes")%>%
  select(Q135, Q27)%>%
  tabyl(Q135, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Payment modalities for smuggling services / Sex","", "",""),align = "l")
```

## S1 - Total amount paid so far for smuggling services

```{r}
getFX("XOF/USD")
cfa_usd <- as.numeric(last(XOFUSD$XOF.USD))

getFX("EUR/USD")
eur_usd <- as.numeric(last(EURUSD$EUR.USD))

getFX("GHS/USD")
ghs_usd <- as.numeric(last(GHSUSD$GHS.USD))

getFX("GNF/USD")
gnf_usd <- as.numeric(last(GNFUSD$GNF.USD))

getFX("NGN/USD")
ngn_usd <- as.numeric(last(NGNUSD$NGN.USD))

df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No" & S1 =="Know the amount" & Q27 =="Male") %>%
  select(S1_1, S1_3) %>%
  mutate(
    S1_3 = as.numeric(S1_3),  # Convert the column to numeric
    S1_3 = case_when(
      S1_1 == "CFA" ~ round(S1_3 * cfa_usd),  # Convert CFA to USD
      S1_1 == "GHS" ~ round(S1_3 * ghs_usd),  # Convert GHS to USD
      S1_1 == "GNF" ~ round(S1_3 * gnf_usd),
      S1_1 == "NGN" ~ round(S1_3 * ngn_usd),
      TRUE ~ S1_3  # Keep the original value for other cases
    )
  ) %>%
  filter(S1_3 != 0)%>%
  summarize(across(S1_3, list(Mean = ~paste0(round(mean(., na.rm = TRUE),2), ' $'),
                              Median = ~paste0(median(., na.rm = TRUE),' $'),
                              Min = ~paste0(min(., na.rm = TRUE),' $'),
                              Max = ~paste0(max(., na.rm = TRUE),' $'))))%>%
  rename_with(~ gsub("S1_3_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(caption = "Male respondents", format = "html",align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Total amount paid so far for smugglers", "", "","N = 697"),align = "l")
  
  
df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No" & S1 =="Know the amount" & Q27 =="Female") %>%
  select(S1_1, S1_3) %>%
  mutate(
    S1_3 = as.numeric(S1_3),  # Convert the column to numeric
    S1_3 = case_when(
      S1_1 == "CFA" ~ round(S1_3 * cfa_usd),  # Convert CFA to USD
      S1_1 == "GHS" ~ round(S1_3 * ghs_usd),  # Convert GHS to USD
      S1_1 == "GNF" ~ round(S1_3 * gnf_usd),
      S1_1 == "NGN" ~ round(S1_3 * ngn_usd),
      TRUE ~ S1_3  # Keep the original value for other cases
    )
  ) %>%
  filter(S1_3 != 0)%>%
  summarize(across(S1_3, list(Mean = ~paste0(round(mean(., na.rm = TRUE),2), ' $'),
                              Median = ~paste0(median(., na.rm = TRUE),' $'),
                              Min = ~paste0(min(., na.rm = TRUE),' $'),
                              Max = ~paste0(max(., na.rm = TRUE),' $'))))%>%
  rename_with(~ gsub("S1_3_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(caption = "Female respondents", format = "html",align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Total amount paid so far for smugglers", "", "","N = 461"),align = "l")

```

## S2/S3/S4 - Total amount paid for smuggling services in installments

```{r}
getFX("XOF/USD")
cfa_usd <- as.numeric(last(XOFUSD$XOF.USD))

getFX("EUR/USD")
eur_usd <- as.numeric(last(EURUSD$EUR.USD))

getFX("GHS/USD")
ghs_usd <- as.numeric(last(GHSUSD$GHS.USD))

getFX("GNF/USD")
gnf_usd <- as.numeric(last(GNFUSD$GNF.USD))

getFX("NGN/USD")
ngn_usd <- as.numeric(last(NGNUSD$NGN.USD))

getFX("SLL/USD")
sll_usd <- as.numeric(last(SLLUSD$SLL.USD))

cbind(df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No" & is.na(S1)) %>%
  select(S2_1,S3_1,S4_1) %>%
  pivot_longer(cols = everything(), values_to = "Currency"),
  df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No" & is.na(S1)) %>%
  select(S2_3,S3_3,S4_3) %>%
  pivot_longer(cols = everything(), values_to = "Amount"))%>%
  select(-name)%>%
  filter(!is.na(Amount))%>%
  mutate(
    Amount = as.numeric(Amount),  # Convert the column to numeric
    Amount = case_when(
      Currency == "CFA" ~ round(Amount * cfa_usd),  # Convert CFA to USD
      Currency == "GHS" ~ round(Amount * ghs_usd),  # Convert GHS to USD
      Currency == "GNF" ~ round(Amount * gnf_usd),
      Currency == "NGN" ~ round(Amount * ngn_usd),
      Currency == "EUR" ~ round(Amount * eur_usd),
      Currency == "SLL" ~ round(Amount * sll_usd),
      TRUE ~ Amount  # Keep the original value for other cases
    )
  ) %>%
  filter(Amount != 0)%>%
  arrange(desc(Amount))%>%
  summarize(across(Amount, list(Mean = ~paste0(round(mean(., na.rm = TRUE),2), ' $'),
                              Median = ~paste0(median(., na.rm = TRUE),' $'),
                              Min = ~paste0(min(., na.rm = TRUE),' $'),
                              Max = ~paste0(max(., na.rm = TRUE),' $'))))%>%
  rename_with(~ gsub("Currency_", "", .)) %>%  
  kable(align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Total amount paid for smuggling services in installments", "", "","N =  only those that know the amount"),align = "l")

```

## Q163 - contact with state officials

```{r}
df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No")%>%
  select(`Q163/Police at a border`: `Q163/None of these`)%>%
  pivot_longer(cols = everything(), values_to = "contact_with_officials")%>%
  select(-name)%>%
  tabyl(contact_with_officials, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(percent))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(colum = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Contact with state officials", "", "N = 1550"),align = "l")


df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No")%>%
  select(Q27,`Q163/Police at a border`: `Q163/None of these`)%>%
  pivot_longer(cols = `Q163/Police at a border`: `Q163/None of these`, values_to = "contact_with_officials")%>%
  select(-name)%>%
  tabyl(show_na = FALSE, contact_with_officials, Q27)%>%
  arrange(desc(Male + Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Contact with state officials", "", "",""),align = "l")
```

## Q164 - corruption

```{r}
df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No")%>%
  select(`Q164/Police at a border`: `Q164/None of these`)%>%
  pivot_longer(cols = everything(), values_to = "contact_with_officials")%>%
  select(-name)%>%
  tabyl(contact_with_officials, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(percent))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(colum = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Corruption with state officials", "", "N = 1550"),align = "l")


df_1 %>%
  filter(smuggler_module_open == "Yes" & Q133 != "No")%>%
  select(Q27,`Q164/Police at a border`: `Q164/None of these`)%>%
  pivot_longer(cols = `Q164/Police at a border`: `Q164/None of these`, values_to = "contact_with_officials")%>%
  select(-name)%>%
  tabyl(show_na = FALSE, contact_with_officials, Q27)%>%
  arrange(desc(Male + Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Corruption with state officials", "", "",""),align = "l")
```

## S11 - Were state officials involved in or did they facilitate migrant smuggling during your journey?

```{r}
df_1 %>%
  filter(Q133 != "No" & smuggler_module_open == "Yes")%>%
  select(S11,Q27)%>%
  tabyl(show_na = FALSE, S11,Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("State officials involvement in smuggling","", "",""),align = "l")
```

# 3- What are the links between reliance on smuggler services and protection risks?

## Dangerous locations

### Traveled through a dangerous location vs those who did not

```{r}
df_1 %>%
  mutate(transited = case_when(
    Q98 == "None" ~ "Did not travel through a dangerous location",
    TRUE ~ "Travelled at least once"
  ))%>%
  tabyl(transited,Q133)%>%
  arrange(desc(Yes + No))%>%
  adorn_totals(where =c("row", "col"))%>%  
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Stopped ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Disaggregated by subset", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

df_1 %>%
  mutate(transited = case_when(
    Q98 == "None" ~ "Did not travel through a dangerous location",
    TRUE ~ "Travelled at least once"
  ))%>%
  tabyl(transited,Q27)%>%
  arrange(desc(Male + Female))%>%
  adorn_totals(where =c("row", "col"))%>%  
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Stopped ", col_name = " Sex", "combined") %>%
  knitr::kable(caption = "Disaggregated by sex", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")


```

### Summary of the number of dangerous locations reported

```{r}
df_stops <- df_1 %>%
  select(Q133,Q98,Q102,Q106,Q110,Q114)%>%
  mutate(count = rowSums(across(everything(), ~ !(. %in% c("Yes", "No", "None", NA )))))


df_stops %>%
  filter(Q133 == "Yes" & count != 0)%>%
  summarize(across(count, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("count_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l", caption = "Stops for those who used a smuggler") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")

df_stops %>%
  filter(Q133 == "No" & count != 0)%>%
  summarize(across(count, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("count_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l", caption = "Stops for those who did not use a smuggler") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

### Q99 ; 103 ; 107 ; 111 ; 115 - Most dangerous location

```{r}
tabyl_ref <- df_1 %>%
  select(Q99,Q103,Q107,Q111,Q115)%>%
  pivot_longer(cols = everything(), values_to = "dangerous_locations")%>%
  filter(dangerous_locations != "Other" & !is.na(dangerous_locations))%>%
  tabyl(dangerous_locations)%>%
  filter(n>20)
  
  
tabyl_ref%>%
  arrange(desc(n))%>%
  adorn_totals()%>%
  mutate(percent = n/2674)%>%
  adorn_pct_formatting(column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Most dangerous locations","", "N= 2674"),align = "l")


df_1%>%
  select(Q133,Q99,Q103,Q107,Q111,Q115)%>%
  pivot_longer(cols = -Q133, values_to = "dangerous_locations")%>%
  filter(dangerous_locations != "Other" & !is.na(dangerous_locations))%>%
  tabyl(dangerous_locations,Q133)%>%
  filter(dangerous_locations %in% tabyl_ref$dangerous_locations)%>%
  arrange(desc(Yes + No))%>%
  adorn_totals()%>%
  knitr :: kable(caption = "Disaggregated by subset", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")


df_1%>%
  select(Q27,Q99,Q103,Q107,Q111,Q115)%>%
  pivot_longer(cols = -Q27, values_to = "dangerous_locations")%>%
  filter(dangerous_locations != "Other" & !is.na(dangerous_locations))%>%
  tabyl(dangerous_locations,Q27)%>%
  filter(dangerous_locations %in% tabyl_ref$dangerous_locations)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals()%>%
  knitr :: kable(caption = "Disaggregated by sex", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")


```

## Q100 ; 104 ; 108 ; 112 ; 116 -Top 5 perceived risks

```{r}
reasons_matrix <- df_1 %>% 
  pivot_longer(`Q100/Death`: `Q100/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None"))

#aggregating the risks for the second stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q104/Death`: `Q104/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the third stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q108/Death`: `Q108/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the fourth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q112/Death`: `Q112/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the fifth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q116/Death`: `Q116/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#Compute frequencies for each reason

reasons_matrix%>%
  tabyl(risks)%>%
  arrange(desc(n))%>%
  mutate(percent = n/1715)%>%
  adorn_pct_formatting(column = "percent") %>%
  #adorn_totals(where = "row")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Top perceived risks", "", "N = 1715"),align = "l")



tabyl_ref <- reasons_matrix%>%
  tabyl(risks, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_ref$Female %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Female)%>%
  adorn_title(row_name = "Risks ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_ref$Male %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Male)%>%
  adorn_title(row_name = "Risks ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table



# #First danger location and perceived risks
# perceived_risks <- df_1 %>%
#   select(Q98, Q99:`Q100/Refused`) %>%
#   select(-matches("_1"), -c(Q100, `Q100/Refused`, `Q100/Other`, Q99_2)) %>%
#   pivot_longer(cols = -c(Q98, Q99),  # Pivot all except Q98 and Q99
#                values_to = "perceived_risks") %>%
#   filter(if_all(c(perceived_risks, Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#   select(-name)
# 
# 
# #aggregating second stop with location and reasons
# 
# perceived_risks <- rbind (perceived_risks, df_1 %>%
#                             select(Q102:`Q104/Refused`) %>%
#                             select(-matches("_1"), -c(Q104, `Q104/Refused`, `Q104/Other`, Q103_2)) %>%
#                             pivot_longer(cols = -c(Q102, Q103),  # Pivot all except Q98 and Q99
#                                          values_to = "perceived_risks") %>%
#                             rename(
#                               Q98 = Q102,
#                               Q99 = Q103)%>%
#                             filter(if_all(c(perceived_risks,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# #aggregating third stop with location and reasons
# 
# perceived_risks <- rbind (perceived_risks, df_1 %>%
#                             select(Q106:`Q108/Refused`) %>%
#                             select(-matches("_1"), -c(Q108, `Q108/Refused`, `Q108/Other`, Q107_2)) %>%
#                             pivot_longer(cols = -c(Q106, Q107),  # Pivot all except Q98 and Q99
#                                          values_to = "perceived_risks") %>%
#                             rename(
#                               Q98 = Q106,
#                               Q99 = Q107)%>%
#                             filter(if_all(c(perceived_risks,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# 
# #aggregating fourth stop with location and reasons
# 
# perceived_risks <- rbind (perceived_risks, df_1 %>%
#                             select(Q110:`Q112/Refused`) %>%
#                             select(-matches("_1"), -c(Q112, `Q112/Refused`, `Q112/Other`, Q111_2)) %>%
#                             pivot_longer(cols = -c(Q110, Q111),  # Pivot all except Q98 and Q99
#                                          values_to = "perceived_risks") %>%
#                             rename(
#                               Q98 = Q110,
#                               Q99 = Q111)%>%
#                             filter(if_all(c(perceived_risks,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# #aggregating fifth stop with location and reasons
# 
# perceived_risks <- rbind (perceived_risks, df_1 %>%
#                             select(Q114:`Q116/Refused`) %>%
#                             select(-matches("_1"), -c(Q116, `Q116/Refused`, `Q116/Other`, Q115_2)) %>%
#                             pivot_longer(cols = -c(Q114, Q115),  # Pivot all except Q98 and Q99
#                                          values_to = "perceived_risks") %>%
#                             rename(
#                               Q98 = Q114,
#                               Q99 = Q115)%>%
#                             filter(if_all(c(perceived_risks,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# perceived_risks <- rename(perceived_risks,
#                       Country = Q98,
#                       Location = Q99) 
# 
# 
# #Compute frequencies for each reason for each country
# perceived_risks %>%
#   group_by(Country, Location, perceived_risks) %>%
#   summarize(frequency = n(), .groups = 'drop') %>%
#   arrange(desc(frequency)) %>%
#   group_by(Country) %>%
#   slice_max(order_by = frequency, n = 5, with_ties = FALSE) %>%  # Ensure only the top 5 per country
#   mutate(percent = frequency /1715)%>% 
#   adorn_pct_formatting(column = "percent")%>%
#   knitr::kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left") %>%
#   add_header_above(header = c("Top 5 perceived risks per country", "", "","", "N= 1715"), align = "l")
```

## Q101 ; 105 ; 109 ; 113 ; 117 - Top 5 likely perpetrators

```{r}
reasons_matrix <- df_1 %>% 
  pivot_longer(`Q101/Smugglers`: `Q101/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None"))

#aggregating the perpetrators for the second stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q105/Smugglers`: `Q105/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the third stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q109/Smugglers`: `Q109/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the fourth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q113/Smugglers`: `Q113/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the fifth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q117/Smugglers`: `Q117/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#Compute frequencies for each reason

reasons_matrix%>%
  tabyl(perpetrators)%>%
  arrange(desc(n))%>%
  mutate(percent = n/1715)%>%
  adorn_pct_formatting(column = "percent") %>%
  #adorn_totals(where = "row")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Top likely perpetrators", "", "N = 1715"),align = "l")



tabyl_ref <- reasons_matrix%>%
  tabyl(perpetrators, Q133, Q27)%>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_ref$Female %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Female)%>%
  adorn_title(row_name = "Perpetrators ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_ref$Male %>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front", ns = tabyl_ref$Male)%>%
  adorn_title(row_name = "Perpetrators ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table



# #First danger location and likely perpetrators
# perpetrators_df <- df_1 %>%
#   select(Q98, Q99,`Q101/Smugglers`:`Q101/Refused`) %>%
#   select(-matches("_1"), -c(`Q101/Refused`, `Q101/Other`)) %>%
#   pivot_longer(cols = -c(Q98, Q99),  # Pivot all except Q98 and Q99
#                values_to = "perpetrators") %>%
#   filter(if_all(c(perpetrators, Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#   select(-name)
# 
# 
# #aggregating second stop with location and likely perpetrators
# 
# perpetrators_df <- rbind (perpetrators_df, df_1 %>%
#                             select(Q102, Q103,`Q105/Smugglers`:`Q105/Refused`) %>%
#                             select(-matches("_1"), -c(`Q105/Refused`, `Q105/Other`)) %>%
#                             pivot_longer(cols = -c(Q102, Q103),  # Pivot all except Q98 and Q99
#                                          values_to = "perpetrators") %>%
#                             rename(
#                               Q98 = Q102,
#                               Q99 = Q103)%>%
#                             filter(if_all(c(perpetrators,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# #aggregating third stop with location and likely perpetrators
# 
# perpetrators_df <- rbind (perpetrators_df, df_1 %>%
#                             select(Q106, Q107,`Q109/Smugglers`:`Q109/Refused`) %>%
#                             select(-matches("_1"), -c(`Q109/Refused`, `Q109/Other`)) %>%
#                             pivot_longer(cols = -c(Q106, Q107),  # Pivot all except Q98 and Q99
#                                          values_to = "perpetrators") %>%
#                             rename(
#                               Q98 = Q106,
#                               Q99 = Q107)%>%
#                             filter(if_all(c(perpetrators,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# 
# #aggregating fourth stop with location and likely perpetrators
# 
# 
# perpetrators_df <- rbind (perpetrators_df, df_1 %>%
#                             select(Q110, Q111,`Q113/Smugglers`:`Q113/Refused`) %>%
#                             select(-matches("_1"), -c(`Q113/Refused`, `Q113/Other`)) %>%
#                             pivot_longer(cols = -c(Q110, Q111),  # Pivot all except Q98 and Q99
#                                          values_to = "perpetrators") %>%
#                             rename(
#                               Q98 = Q110,
#                               Q99 = Q111)%>%
#                             filter(if_all(c(perpetrators,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# #aggregating fifth stop with location and likely perpetrators
# 
# perpetrators_df <- rbind (perpetrators_df, df_1 %>%
#                             select(Q114, Q115,`Q117/Smugglers`:`Q117/Refused`) %>%
#                             select(-matches("_1"), -c(`Q117/Refused`, `Q117/Other`)) %>%
#                             pivot_longer(cols = -c(Q114, Q115),  # Pivot all except Q98 and Q99
#                                          values_to = "perpetrators") %>%
#                             rename(
#                               Q98 = Q114,
#                               Q99 = Q115)%>%
#                             filter(if_all(c(perpetrators,  Q99), ~ !is.na(.) & . != "None" & . != "Other")) %>%
#                             select(-name))
# 
# perpetrators_df <- rename(perpetrators_df,
#                           Country = Q98,
#                           Location = Q99) 
# 
# 
# #Compute frequencies for  likely perpetrators for each country
# perpetrators_df %>%
#   group_by(Country, Location, perpetrators) %>%
#   summarize(frequency = n(), .groups = 'drop') %>%
#   arrange(desc(frequency)) %>%
#   group_by(Country) %>%
#   slice_max(order_by = frequency, n = 5, with_ties = FALSE) %>%  # Ensure only the top 5 per country
#   mutate(percent = frequency /1715)%>% 
#   adorn_pct_formatting(column = "percent")%>%
#   knitr::kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left") %>%
#   add_header_above(header = c("Top 5 likely perpetrators per country", "", "","", "N= 1715"), align = "l")
```

## Q118 - Have you personally experienced any of these types of incidents on your journey?

```{r}
df_1 %>%
  select(`Q118/Witnessed death`: `Q118/None`)%>%
  pivot_longer(cols = everything(), values_to = "experienced_incidents")%>%
  select(-name)%>%
  tabyl(experienced_incidents, show_na = FALSE)%>%
  arrange(desc(n))%>%
  mutate(percent = n / 1170)%>%
  adorn_pct_formatting( column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Experienced incidents", "", "N = 1170"),align = "l")


tabyl_ref <- df_1 %>%
  select(Q133, Q27,`Q118/Witnessed death`: `Q118/None`)%>%
  pivot_longer(cols = -c(Q133,Q27), values_to = "experienced_incidents")%>%
  select(-name)

tabyl_result <- tabyl_ref %>%
  tabyl(show_na = FALSE,experienced_incidents,Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Experienced incidents ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Experienced incidents ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

N = are the people that were asked this question

## Q123 - Did you receive assistance along the way?

```{r}
df_1 %>%
  tabyl(Q123)%>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Did you receive assistance along the way?","", ""),align = "l")


tabyl_result <- df_1 %>%
  tabyl(show_na = FALSE,Q123,Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Received assistance? ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Received assistance? ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q124 - What kind of assistance did you receive?

```{r}
df_1 %>%
  select(`Q124/Shelter`: `Q124/Access to work`)%>%
  pivot_longer(cols = everything(), values_to = "assistance_received")%>%
  select(-name)%>%
  tabyl(assistance_received, show_na = FALSE)%>%
  mutate(percent = n / 1387)%>%
  arrange(desc(n))%>%
  adorn_pct_formatting(column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Received assistance", "", "N= 1387"),align = "l")


tabyl_ref <- df_1 %>%
  select(Q133, Q27,`Q124/Shelter`: `Q124/Access to work`)%>%
  pivot_longer(cols = -c(Q133,Q27), values_to = "assistance_received")%>%
  select(-name)

tabyl_result <- tabyl_ref %>%
  tabyl(show_na = FALSE,assistance_received,Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Received assistance ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Received assistance ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q125 - Who did you receive assistance from?

```{r}
df_1 %>%
  select(`Q125/The government`: `Q125/Smugglers`)%>%
  pivot_longer(cols = everything(), values_to = "assistance_provider")%>%
  select(-name)%>%
  tabyl(assistance_provider, show_na = FALSE)%>%
  mutate(percent = n / 1387)%>%
  arrange(desc(n))%>%
  #adorn_totals()%>%
  adorn_pct_formatting(column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Assitance providers", "", "N= 1387"),align = "l")

tabyl_ref <- df_1 %>%
  select(Q133, Q27,`Q125/The government`: `Q125/Smugglers`)%>%
  pivot_longer(cols = -c(Q133,Q27), values_to = "assistance_provider")%>%
  select(-name)

tabyl_result <- tabyl_ref %>%
  tabyl(show_na = FALSE,assistance_provider,Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Assitance providers ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Assitance providers ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q129 - Do you need more assistance now?

```{r}
df_1 %>% 
  tabyl(Q129, show_na = FALSE) %>%
  arrange(desc(n))%>%
  adorn_totals(where = "row")%>%
  adorn_pct_formatting() %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Need for assistance currently", "", ""),align = "l")


tabyl_result <- df_1 %>%
  tabyl(show_na = FALSE, Q129, Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Need for assistance currently ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Need for assistance currently ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## Q130 - What kind of assistance do you need?

```{r}
df_1 %>%
  select(`Q130/Shelter`: `Q130/Access to work`)%>%
  pivot_longer(cols = everything(), values_to = "assistance_needs")%>%
  select(-name)%>%
  tabyl(assistance_needs, show_na = FALSE)%>%
  mutate(percent = n / 2338)%>%
  arrange(desc(n))%>%
  #adorn_totals()%>%
  adorn_pct_formatting(column = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Type of assistance needed currently", "", "N= 2338"),align = "l")

tabyl_ref <- df_1 %>%
  select(Q133, Q27,`Q130/Shelter`: `Q130/Access to work`)%>%
  pivot_longer(cols = -c(Q133,Q27), values_to = "assistance_needs")%>%
  select(-name)

tabyl_result <- tabyl_ref %>%
  tabyl(show_na = FALSE,assistance_needs,Q133, Q27) %>%
  lapply(function(df) arrange(df, desc(Yes + No)))%>%
  adorn_totals(where =c("row", "col"))


# Format the Female table
female_table <- tabyl_result$Female %>%  
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Type of assistance needed currently ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Type of assistance needed currently ", col_name = " Smuggler use", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

male_table
female_table
```

## CANCELLED

### Q126/Q127 - Places where assistance was needed the most and not received

```{r}

# df_1 %>%
#   select(Q14,Q127)%>%
#   filter(!(is.na(Q127)))%>%
#   group_by(Q14,Q127)%>%
#   summarize(frequency = n())%>%
#   arrange(desc(frequency))%>%
#   
#   tabyl(show_na = FALSE, Q127,Q14)
  



# df_1 %>%
#   select(Q126, Q127)%>%
#   filter(Q126 != "None")%>%
#   group_by(Q126,Q127)%>%
#   summarize( frequency = n())%>%
#   arrange(desc(frequency))%>%
#   adorn_totals(where = "row")%>%
#   mutate(percent = frequency / 1019)%>%
#   adorn_pct_formatting(column = "percent")%>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = TRUE, 
#                 position = "left")%>%
#   add_header_above(header = c("Places where assistance \n was needed the most and not received", "", "removed NAs",""),align = "l")
```

### Q128: Most needed assistance en route

```{r}
# df_1 %>%
#   select(`Q128/Shelter`: `Q128/Refused`)%>%
#   select(-`Q128/Other`)%>%
#   pivot_longer(cols = everything(), values_to = "most_needed_assistance")%>%
#   select(-name)%>%
#   tabyl(most_needed_assistance, show_na = FALSE)%>%
#   arrange(desc(n))%>%
#   adorn_totals()%>%
#   adorn_pct_formatting() %>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
#                 full_width = TRUE,
#                 position = "left")%>%
#   add_header_above(header = c("Most needed assistance en route", "", ""),align = "l")
```
