---
title: "Gender Snapshot"
editor: visual
date: "`r Sys.Date()`"

format: 
  html:
    toc: true  # Enable table of contents
    toc-title: "Table of Content"  # Set the title of the ToC
    toc-depth: 3  # Set the depth of headers (h1 and h2)
    toc-location: right
    embed-resources: true
    smooth-scroll: true
    lightbox: true

execute:
  echo: false      # Hide code
  warning: false   # Hide warnings
  message: false   # Hide messages
  results: hide    # Hide output
  
theme:
  light: flatly
  dark: darkly
---

```{r}
#| echo: false
#| results: hide
#| message: false
#| warning: false
library(readxl)
library(writexl)
library(janitor)
library(dplyr)
library(tidyr)
library(janitor)
#install.packages("ggplot2")
#install.packages("kableExtra")
library(kableExtra)
library(knitr)
library(lubridate)
library(stringr)
#install.packages("quantmod")
library(quantmod)
#install.packages("outliers")
library(outliers)
library(ggplot2)
library(htmltools)

#Loading the data frame
df <- read_excel("../Samples/gender_snapshot.xlsx", col_names = FALSE)

#Setting up the data frame

titles <- df[1:2,]

colnames(df) <- df [2,]

df_1 <- df[-c(1,2),]

#converting all numeric date variables to dates

df_1 <- df_1 %>% 
  mutate(across(c(`_submission_time`,today, Q45_1, Q25,Q165, Q141_3, S1_3, S2_3, S3_3, S4_3), ~ as.numeric(.))) %>%
  mutate(across(c(`_submission_time`,today, Q45_1), ~ excel_numeric_to_date(.)))%>%
  mutate(Q133 = ifelse(grepl("^Yes",Q133), "Yes", Q133))%>%
  mutate(Q14 = if_else(Q14 == "Sikasso", "Sikasso city", Q14))%>%
  mutate(Q25 = if_else(Q25<30, "[18,30)","[30,65)"))
```

# Grouping Variables

```{r}
df_1 %>% 
  tabyl(Q25, Q27) %>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  
  #Nice formatting
  adorn_title(row_name = "Age group", col_name = "Gender", "combined") %>%
  
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Grouping Variables","","",""),align = "l")
```

# Profiling

## Q13 - country of interview

```{r}
df_1 %>% 
  tabyl(Q13,Q27) %>%
  arrange(desc(Male+Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country ", col_name = " Sex", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")


tabyl_result <- df_1 %>%
  tabyl(Q13, Q25, Q27) 

# Format the Female table
female_table <- tabyl_result$Female %>%
  arrange(desc(`[18,30)`+ `[30,65)`))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country ", col_name = " Age group", "combined") %>%
  knitr::kable(caption = "Female Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")

# Format the Male table
male_table <- tabyl_result$Male %>%
  arrange(desc(`[18,30)`+ `[30,65)`))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country ", col_name = " Age group", "combined") %>%
  knitr::kable(caption = "Male Respondents", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
male_table
female_table
```

## Q14 - Place of interview

```{r}
df_1 %>%
  tabyl(Q14,Q27)  %>%
  arrange(desc(Male+Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Place of interview ", col_name = " Sex", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")





# total_tabyl <- df_1 %>%
#   tabyl(Q14) %>%
#   arrange(desc(n))%>%
#   adorn_totals(where = "row")%>%
#   adorn_pct_formatting() %>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = TRUE, 
#                 position = "left")%>%
#   add_header_above(header = c("Place of interview", "", ""),align = "l")
# 
# # Format the Female table
# female_table <- tabyl_result$Female %>%
#   arrange(desc(Yes+No))%>%
#   adorn_totals(where = c("row", "col"))%>%
#   adorn_percentages(denominator = "col") %>%
#   adorn_pct_formatting() %>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Location ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Female Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# 
# # Format the Male table
# male_table <- tabyl_result$Male %>%
#   arrange(desc(Yes+No))%>%
#   adorn_totals(where = c("row", "col"))%>%
#   adorn_percentages(denominator = "col") %>%
#   adorn_pct_formatting() %>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Location ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Male Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# total_tabyl
# male_table
# female_table

```

## Q25 - Age - Summary

```{r}
df_1 %>%
  summarize(across(Q25, list(Mean = ~mean(., na.rm = TRUE),
                             Median = ~median(., na.rm = TRUE),
                             Min = ~min(., na.rm = TRUE),
                             Max = ~max(., na.rm = TRUE))))%>%
  rename_with(~ gsub("Q25_", "", .)) %>%  # Remove the "Q25_" prefix
  kable(align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Age", "", "",""),align = "l")

df_age <- df_1 %>%
  filter(!is.na(Q25))

# Create age groups (e.g., 5-year intervals)
df_age <- df_age %>%
  mutate(age_group = cut(Q25, breaks = seq(0, 100, by = 5), right = FALSE))

# Summarize the data by age group
df_age_summary <- df_age %>%
  group_by(age_group, Q27) %>%
  summarise(count = n()) %>%
  ungroup()
# Create a mirrored layout by making the count for one sex negative (e.g., Female)
df_age_summary <- df_age_summary %>%
  mutate(count = ifelse(Q27 == "Female", -count, count))  # Negative count for Female
```

------------------------------------------------------------------------

```{r}



# 
# 
#   geom_bar(stat = "identity", position = "identity") +
#   
#   coord_flip() +  # Flip coordinates for horizontal bars
#   scale_y_continuous(labels = abs, seq(-60, 60, by = 100)) +
#   
#   # Customize the fill colors: change red to light violet
#   scale_fill_manual(values = c("Female" = "#D8BFD8", "Male" = "#00CED1")) +
#   
#   # Labels
#   labs(
#     title = "Age Distribution of Respondents by Sex",
#     x = "Age Group",
#     y = "Number of Respondents",
#     fill = "Sex"
#   ) +
#   
#   # Customize the theme: Legend beneath the x-axis title and justified to the left
#   theme_minimal() +
#   theme(
#     legend.title = element_blank(),  # Hide the "Group" label in the legend
#     legend.position = "bottom",  # Move the legend to the bottom
#     legend.direction = "horizontal",  # Set legend to be horizontal
#     plot.title = element_text(hjust = 0.45),  # Center-align title
#     axis.text.y = element_text(size = 10),  # Adjust y-axis text size
#     axis.title.x = element_text(margin = margin(t = 15)),  # Add margin to the x-axis title
#     axis.title.y = element_text(margin = margin(r = 15)),   # Add margin to the y-axis title
#     plot.margin = margin(10, 10, 20, 10)  # Add margin below the plot for the legend
#   )
# Create the pyramid plot with sex disaggregation and centered x-axis
ggplot(df_age_summary, aes(x = age_group, y = count, fill = Q27)) +
  geom_bar(stat = "identity", position = "identity") + 
  coord_flip() +  # Plot the bars
  
  # Add numbers on the bars with a darker color
  geom_text(aes(label = abs(count)), hjust = ifelse(df_age_summary$count < 0, 1.1, -0.1), 
            size = 4, alpha = 0.9, color = "black") +  # Darken the text
  
  # Center the x-axis
scale_y_continuous(labels = abs, limits = c(-250, 350), expand = expansion(mult = c(0.05, 0.05))) +  # Extend axis limits
  
  labs(
    title = "Age Distribution",
    x = "Age Group",
    y = "Number of Respondents",
    fill = "Sex"
  ) +
  
  theme_minimal() +
  scale_fill_manual(values = c("Female" = "#DDA0DD", "Male" = "#00CED1")) +  # Colors for each sex
  
  theme(
    legend.title = element_blank(),  # Hide the "Group" label in the legend
    legend.position = "bottom",  # Move the legend to the bottom
    legend.direction = "horizontal",  # Set legend to be horizontal
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),  # Center-align and bold title
    axis.text.y = element_text(size = 10, margin = margin(r=0), hjust = 1),  # Adjust y-axis text size
    axis.title.x = element_text(margin = margin(t = 15), hjust = 0.40),  # Center-align x-axis title
    axis.title.y = element_text(margin = margin(r = 25)),  # Move y-axis further from the chart
    plot.margin = margin(10, 20, 20, 10),  # Add margin to move content away from the edges
    plot.title.position = "plot",  # Ensure title aligns properly
    legend.location = "plot" 
  )

```

## Q30 - Dependent children

```{r}

df_1 %>%
  tabyl(Q30,Q27)  %>%
  arrange(desc(Male+Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Carrying dependent children ", col_name = " Sex", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")





# tabyl_result <- df_1 %>%
#   tabyl(Q30, Q133, Q27) 
# 
# total_tabyl <- df_1 %>%
#   tabyl(Q30) %>%
#   adorn_totals(where = "row")%>%
#   adorn_pct_formatting() %>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = TRUE, 
#                 position = "left")%>%
#   add_header_above(header = c("Carrying dependent children", "", ""),align = "l")
# 
# # Format the Female table
# female_table <- tabyl_result$Female %>%  
#   adorn_totals(where = c("row", "col"))%>%
#   adorn_percentages(denominator = "col") %>%
#   adorn_pct_formatting() %>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Carrying dependent children ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Female Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# 
# # Format the Male table
# male_table <- tabyl_result$Male %>%
#   adorn_totals(where = c("row", "col"))%>%
#   adorn_percentages(denominator = "col") %>%
#   adorn_pct_formatting() %>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Carrying dependent children ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Male Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# total_tabyl
# male_table
# female_table
```

## Q31 - country of origin

```{r}

df_1 %>%
  tabyl(Q31,Q27)  %>%
  arrange(desc(Male+Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Country of origin ", col_name = " Sex", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")




# tabyl_result <- df_1 %>%
#   filter(Q31 %in% c("Togo","Nigeria", "Côte d'Ivoire", "Benin", "Niger"))%>%
#   tabyl(Q31, Q133, Q27)
# 
# total_tabyl <- df_1 %>%
#   tabyl(Q31) %>%
#   arrange(desc(n))%>%
#   head(5)%>%
#   adorn_totals(where = "row")%>%
#   adorn_pct_formatting() %>%
#   knitr :: kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = TRUE, 
#                 position = "left")%>%
#   add_header_above(header = c("Country of origin", "", "N = 2674"),align = "l")
# 
# # Format the Female table
# female_table <- tabyl_result$Female %>%
#   arrange(desc(Yes+No))%>%
#   adorn_totals(where =c("row", "col"))%>%
#   adorn_percentages(denominator = "col")%>%
#   adorn_pct_formatting()%>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Country of origin ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Female Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# 
# # Format the Male table
# male_table <- tabyl_result$Male %>%
#   arrange(desc(Yes+No))%>%
#   adorn_totals(where =c("row", "col"))%>%
#   adorn_percentages(denominator = "col")%>%
#   adorn_pct_formatting()%>%
#   adorn_ns(position = "front")%>%
#   adorn_title(row_name = "Country of origin ", col_name = " Smuggler use", "combined") %>%
#   knitr::kable(caption = "Male Respondents", format = "html") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
#                 full_width = FALSE, 
#                 position = "left")
# total_tabyl
# male_table
# female_table


```

## Q33 - migration status

```{r}
df_1 %>%
  tabyl(Q33,Q27)  %>%
  arrange(desc(Male+Female))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "all") %>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Migration status ", col_name = " Sex", "combined") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")
```

# 1- Contact

## a - **How does gender influence contacts between smugglers and migrants?**

### S5: "You mentioned using several smugglers. Were they working together?"

```{r}

df_1 %>%
  tabyl(show_na = FALSE,S5,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Smugglers working together / Sex", "", "", ""),align = "l")
```

### S6: "Did you plan to use a smuggler(s) when preparing your journey?"

```{r}
df_1 %>%
  tabyl(show_na = FALSE,S6,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages()%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("predeparture intentions for using smuggling services / Sex", "", "", ""),align = "l")
```

### S8: "How did you first get in touch with the initial smuggler?"

```{r}
df_1 %>%
  tabyl(show_na = FALSE,S8,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages()%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Initial contact with a smuggler / Sex", "", "", ""),align = "l")
```

### Q135: "How did you pay the smuggler?"

```{r}
df_1 %>%
  select(Q135, Q27)%>%
  tabyl(Q135, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Payment modalities for smuggling services / Sex","", "",""),align = "l")
```

# 2 - Types of services used

## b - **How does gender influence the type of smuggling services used along migration routes?**

### Q133: "Did you use a smuggler?"

```{r}
  df[-c(1,2),] %>% 
    mutate(across(c(`_submission_time`,today, Q45_1, Q25,Q165, Q141_3, S1_3, S2_3, S3_3, S4_3), ~ as.numeric(.))) %>%
  mutate(across(c(`_submission_time`,today, Q45_1), ~ excel_numeric_to_date(.)))%>%
  mutate(Q14 = if_else(Q14 == "Sikasso", "Sikasso city", Q14))%>%
  select(Q133, Q27)%>%
  tabyl(Q133, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Use of a smuggler / Sex","", "",""),align = "l")
```

### Q134: "What did the smuggler provide you with?"

```{r}
df_1 %>%
  select(`Q134/Provision of documents`:`Q134/Helped me find a job`)  %>%
  pivot_longer(cols = everything(), values_to = "Types_smuggler_services")%>%
  tabyl(show_na = FALSE, Types_smuggler_services)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Types of smuggler services", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`Q134/Provision of documents`:`Q134/Helped me find a job`)  %>%
  pivot_longer(cols = -Q27, values_to = "Types_smuggler_services")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, Types_smuggler_services,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Types_smuggler_services / Sex", "", "", "Removed NAs"),align = "l")
```

### S7: "Why did you use a smuggler?"

```{r}
df_1 %>%
  select(`S7/I thought it would be cheaper`:`S7/The smuggler pressured me into it`)  %>%
  pivot_longer(cols = everything(), values_to = "Reasons_for_using_smugglers")%>%
  tabyl(Reasons_for_using_smugglers, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Reasons for using smugglers", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`S7/I thought it would be cheaper`:`S7/The smuggler pressured me into it`)  %>%
  pivot_longer(cols = -Q27, values_to = "Reasons_for_using_smugglers")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, Reasons_for_using_smugglers,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Reasons for using smuggler / Sex", "", "", "Removed NAs"),align = "l")
```

### S10: "Did you use a smuggler to get across any borders between countries?"

```{r}
df_1 %>%
  select(S10, Q27)%>%
  tabyl(S10, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Smuggler use for border crossing / Sex","", "",""),align = "l")
```

### Q145: "What means did you use to obtain information before you left?"

```{r}
df_1 %>%
  select(`Q145/Street advertising (billboards, leafleting)`:`Q145/Phone call`)  %>%
  pivot_longer(cols = everything(), values_to = "means_of_information")%>%
  tabyl(means_of_information, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`Q145/Street advertising (billboards, leafleting)`:`Q145/Phone call`)  %>%
  pivot_longer(cols = -Q27, values_to = "means_of_information")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, means_of_information,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information / Sex", "", "", "Removed NAs"),align = "l")
```

### Q147: "What were your sources of information about routes, destinations, costs, risks...,during your journey ?"

```{r}
df_1 %>%
  select(`Q147/Friends / family in country of departure`:`Q147/Returned migrants`)  %>%
  pivot_longer(cols = everything(), values_to = "means_of_information")%>%
  tabyl(means_of_information, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`Q147/Friends / family in country of departure`:`Q147/Returned migrants`)  %>%
  pivot_longer(cols = -Q27, values_to = "means_of_information")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, means_of_information,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information / Sex", "", "", "Removed NAs"),align = "l")
```

### Q148: "What means did you use to obtain information during your journey ?"

```{r}
df_1 %>%
  select(`Q148/Street advertising (billboards, leafleting)`:`Q148/Phone call`)  %>%
  pivot_longer(cols = everything(), values_to = "means_of_information")%>%
  tabyl(means_of_information, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`Q148/Street advertising (billboards, leafleting)`:`Q148/Phone call`)  %>%
  pivot_longer(cols = -Q27, values_to = "means_of_information")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, means_of_information,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Means of information / Sex", "", "", "Removed NAs"),align = "l")
```

## c- **What are the differences in perceived risks and perceptions of smuggling services between women and men users?**

### i. Risks

#### Q98: "What was the most dangerous location on your journey?

```{r}
df_1 %>%
  mutate(transited = case_when(
    Q98 == "None" ~ "Did not travel through a dangerous location",
    TRUE ~ "Travelled at least once"
  ))%>%
  tabyl(transited,Q27)%>%
  arrange(desc(Male + Female))%>%
  adorn_totals(where =c("row", "col"))%>%  
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting()%>%
  adorn_ns(position = "front")%>%
  adorn_title(row_name = "Stopped ", col_name = " Sex", "combined") %>%
  knitr::kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, 
                position = "left")
```

#### Q100, Q104, Q108, Q112, Q116: "What were the main risks?"

For this variable, the numbers that are below represent the risks that were mentioned at least once.

```{r}
reasons_matrix <- df_1 %>% 
  pivot_longer(`Q100/Death`: `Q100/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(`_id`,Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None"))

#aggregating the risks for the second stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q104/Death`: `Q104/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(`_id`,Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the third stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q108/Death`: `Q108/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(`_id`,Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the fourth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q112/Death`: `Q112/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(`_id`,Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )


#aggregating the risks for the fifth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q116/Death`: `Q116/Injury / ill-health from harsh conditions`, values_to = "risks") %>%
  select(`_id`,Q27, Q133,risks)%>%
  filter(if_all(c(risks), ~ !is.na(.) & . != "None")) )%>%
distinct(`_id`, risks , .keep_all = TRUE)


#Compute frequencies for each reason

reasons_matrix%>%
  tabyl(risks)%>%
  arrange(desc(n))%>%
  mutate(percent = n/771)%>%
  adorn_pct_formatting(column = "percent") %>%
  #adorn_totals(where = "row")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Perceived risks that were mentioned at least once", "", "N = 771"),align = "l")

```

#### Q101, Q105, Q109, Q113, Q117: "Who were likely to be perpetrating such incidents?"

For this variable, the numbers represent the aggregate frequency of all perpetrators mentioned.

```{r}
reasons_matrix <- df_1 %>% 
  pivot_longer(`Q101/Smugglers`: `Q101/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None"))

#aggregating the perpetrators for the second stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q105/Smugglers`: `Q105/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the third stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q109/Smugglers`: `Q109/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the fourth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q113/Smugglers`: `Q113/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#aggregating the perpetrators for the fifth stop

reasons_matrix <- rbind(reasons_matrix, df_1 %>% 
  pivot_longer(`Q117/Smugglers`: `Q117/People from local community`, values_to = "perpetrators") %>%
  select(Q27, Q133,perpetrators)%>%
  filter(if_all(c(perpetrators), ~ !is.na(.) & . != "None")) )


#Compute frequencies for each reason

reasons_matrix%>%
  tabyl(perpetrators)%>%
  arrange(desc(n))%>%
  mutate(percent = n/771)%>%
  adorn_pct_formatting(column = "percent") %>%
  #adorn_totals(where = "row")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Top likely perpetrators", "", "N = 771"),align = "l")
```

### ii. Perception of smugglers

#### Q136: " To what extent do you agree with the following statement: "I was intentionally misled about the journey by my smuggler or smugglers" "

```{r}
df_1 %>%
  select(Q136, Q27)%>%
  tabyl(Q136, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Negative perception of smuggler / Sex","", "",""),align = "l")
```

#### Q137: " To what extent do you agree with the following statement: "The smuggler or smugglers I used helped me in achieving my goal of migrating to another country" "

```{r}
df_1 %>%
  select(Q137, Q27)%>%
  tabyl(Q137, Q27)%>%
  arrange(desc(Female+Male))%>%
  adorn_totals(where = c("row","col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Positive perception of smuggler / Sex","", "",""),align = "l")
```

#### S12: "How would you describe your smuggler or smugglers?"

```{r}
df_1 %>%
  select(`S12/Service provider /business person`:`S12/Friend`)  %>%
  pivot_longer(cols = everything(), values_to = "perception")%>%
  tabyl(perception, show_na = FALSE)%>%
  mutate(percent = n/1550)%>%
  arrange(desc(n))%>%
  
  #adorn_totals(where = "row")%>%
  adorn_pct_formatting(columns = "percent") %>%
  knitr :: kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Perception of smuggler", "", "N = 1550"),align = "l")


df_1 %>%
  select(Q27,`S12/Service provider /business person`:`S12/Friend`)  %>%
  pivot_longer(cols = -Q27, values_to = "perception")%>%
  select (-name)%>%
  tabyl(show_na = FALSE, perception,Q27)%>%
  arrange(desc(Female + Male))%>%
  adorn_totals(where = c("row", "col"))%>%
  adorn_percentages(denominator = "col")%>%
  adorn_pct_formatting() %>%
  adorn_ns(position = "front")%>%
  knitr :: kable(caption = "Disaggregated by sex", format= "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = TRUE, 
                position = "left")%>%
  add_header_above(header = c("Perception of smuggler / Sex", "", "", "Removed NAs"),align = "l")
```
